### 2015-05-26 Appendix/Appendix1.Rnw
Fix path and push pdf

<<results, echo=FALSE, include=FALSE>>=
load("C:\\Users\\Karsten\\Dropbox\\Dissertation\\CurriculumStudy\\SimulationStudy\\SimulationResults.RData")
library(plyr)
eta <- (0:5)/10
results <- ldply(1:6, function(x) data.frame(eta=eta[x], resultlist[[x]]))
# beta1s and beta2s are actually tau1 and tau2
simresults = ddply(results, .(eta), summarise,
      trt1=mean(beta1s),
      trt2=mean(beta2s),
      type1.1=mean(pval1s<0.05),
      type1.2=mean(pval2s<0.05),      
      betamidterm1s = mean(betamidterm1s),
      pvalmidterms1s = mean(pvalmidterm1s),
      sebetamidterm1s = mean(SEbetamidterm1s),
      betamidterm2s = mean(betamidterm2s),
      pvalmidterms2s = mean(pvalmidterm2s),
      sebetamidterm2s = mean(SEbetamidterm2s),
      avgpillai = mean(pillais),
      avgpillaipval = mean(pillaipvals),
      sebeta1s = mean(SEbeta1s),
      sebeta2s = mean(SEbeta1s),
      sdbeta1 = sd(beta1s),
      sdbeta2 = sd(beta2s)
)

>>>>

<<results, echo=FALSE, include=FALSE>>=
load("SimulationResults.RData")
library(plyr)
eta <- (0:5)/10
results <- ldply(1:6, function(x) data.frame(eta=eta[x], resultlist[[x]]))
# beta1s and beta2s are actually tau1 and tau2
simresults = ddply(results, .(eta), summarise,
      trt1=mean(beta1s),
      trt2=mean(beta2s),
      type1.1=mean(pval1s<0.05),
      type1.2=mean(pval2s<0.05),      
      betamidterm1s = mean(betamidterm1s),
      pvalmidterms1s = mean(pvalmidterm1s),
      sebetamidterm1s = mean(SEbetamidterm1s),
      betamidterm2s = mean(betamidterm2s),
      pvalmidterms2s = mean(pvalmidterm2s),
      sebetamidterm2s = mean(SEbetamidterm2s),
      avgpillai = mean(pillais),
      avgpillaipval = mean(pillaipvals),
      sebeta1s = mean(SEbeta1s),
      sebeta2s = mean(SEbeta1s),
      sdbeta1 = sd(beta1s),
      sdbeta2 = sd(beta2s)
)
